### 2009-01-31 articles/2009/geoinformatics/article.tex
misspell
git-svn-id: https://svn.osgeo.org/qgis/trunk@10060 c8812cc2-4d05-0410-92ff-de0c093fc19c

\subsection{Who uses QGIS}
QGIS is now widely used by professionals, government and local agencies, universities and students, and amateurs alike, for a large variety of tasks, from simply viewing raster and vector data (especially useful is the capability to deal with PostGIS layers) to running complex and custom analyses through GRASS modules. Often is used to replace or integrate proprietary software, and several migrations have been accomplished or are underway, both in small and in large companies and public administrations. Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged very intuitive. No doubt thanks to its free and open source licence, it is also used in some of the poorest countries, thus helping to reduce the world digital divde and bring more geoinformatic knowledge where local conditions are more difficult.
Professional support is provided by several companies.

@@

The authors of this article are QGIS Project Steering Committee Members:

>>>>

\subsection{Who uses QGIS}
QGIS is now widely used by professionals, government and local agencies, universities and students, and amateurs alike, for a large variety of tasks, from simply viewing raster and vector data (especially useful is the capability to deal with PostGIS layers) to running complex and custom analyses through GRASS modules. Often is used to replace or integrate proprietary software, and several migrations have been accomplished or are underway, both in small and in large companies and public administrations. Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged very intuitive. No doubt thanks to its free and open source licence, it is also used in some of the poorest countries, thus helping to reduce the world digital divide and bring more geoinformatic knowledge where local conditions are more difficult.
Professional support is provided by several companies.

@@

The authors of this article are the QGIS Project Steering Committee Members:
